How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-03-24 tse-paper/content.tex
Complete Lit survey protocol

We did a second filter phase by downloading the remaining papers,
reading their abstracts, and searching the full text for the
occurrence of ``log''. If these papers contained traces of working
with build logs, we included them in our survey.

%todo: fill-in number
Wtih these X remaining articles, we followed a backward snowball
sampling for other related work referenced in the paragraphs that
mention the technique. This added four papers (five before duplicate
elimination) to our literature set.

>>>>

We did a second filter phase by downloading the surviving papers,
reading their abstracts, and searching the full text for the
occurrence of ``log''. If these papers contained traces of working
with build logs, we included them in our survey.

Wtih these 259 remaining articles, we followed a backward snowball
sampling for related work referenced in the paragraphs that mention
the technique. This added two papers (five before duplicate
elimination and second-pass filtering) to our literature set, both of
which stem from the same first author, were borderline-includes, and
had called build logs from the Linux kernel ``build traces.''
